---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


# The `eurocontrol` package

<!-- badges: start -->
<!-- badges: end -->

The goal of the `eurocontrol` package is to provide helper functions to the
Agency's employees for setup, data retrieval from internal databases, ... .


## Installation

You can install the development version of the `eurocontrol` package
from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("eurocontrol/eurocontrol")
```

**NOTE**: This package (hiddenly) depends on the `ROracle` package, please have
it installed according to the guidelines as published
[here](https://github.com/euctrl-pru/howto/wiki/Tools-Installation-and-Setup-%28For-R%29#roracle).

## Setup

Some of the functions in this package access data from EUROCONTROL's internal Oracle schemes
(maintained by PRISME group.)
The code relies on having the relevant credentials stored in specifically named
environment variables.
The pattern for the environment variable names is

    XXXX_DBNAME 
    XXXX_PWD
    XXXX_USR

where `XXXX` is something like `PRU_DEV`, `PRU_PROD`, ... as defined in the AIU.
Of course other accounts/schemes with access to the underlying tables can be used and encoded
in custom environment variables following the pattern above. The details about which tables are
accessed can be found in the relevant functions documentation.

## Example

A typical use case is to retrieve a list of flights operated in the
area managed by EUROCONTROL's Network Manager.

For example for the flight list of March 2023 you can run (you need access and setup for `PRU_DEV` schema):

```{r example, eval=FALSE}
library(eurocontrol)

flights_tidy(wef = "2023-01-01", til = "2023-04-01")
```



# Development

In order to build the relevant `pkgdown` web pages, execute the following code:

```{r, eval=FALSE}

# How to build the pkgdown from behind proxied Internet
library(withr)
library(pkgdown)

with_options(list(pkgdown.internet = FALSE),
             build_site())


```


